Localisation and Sensor Privacy Using the Extended Information Filter and Secure Weighted Aggregation\thanksref{footnoteinfo}

### 2020-08-25 main.tex
Wrote up our scheme, started on proof write up as well Found ERROR in game/proof - with current game cannot A' cannot provide correct queries to C - next need to update LCAO game and add additional query GetWeights - this will fix both the accuracy of the game to the security requirement as well as allow the proof to proceed as planned Added a header comment Found problem with including microtype package - some incompatibility, need to fix at some stage

% User imported packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{tikz}

@@

%  .d8888b.                            888                 8888888b.                  888 d8b
% d88P  Y88b                           888                 888   Y88b                 888 Y8P
% 888    888                           888                 888    888                 888
% 888        888d888 888  888 88888b.  888888 .d88b.       888   d88P 888d888 .d88b.  888 888 88888b.d88b.
% 888        888P"   888  888 888 "88b 888   d88""88b      8888888P"  888P"  d8P  Y8b 888 888 888 "888 "88b
% 888    888 888     888  888 888  888 888   888  888      888        888    88888888 888 888 888  888  888
% Y88b  d88P 888     Y88b 888 888 d88P Y88b. Y88..88P      888        888    Y8b.     888 888 888  888  888
%  "Y8888P"  888      "Y88888 88888P"   "Y888 "Y88P"       888        888     "Y8888  888 888 888  888  888
%                         888 888
%                    Y8b d88P 888
%                     "Y88P"  888
\section{Cryptography Preliminaries}
When defining our system security requirements and encryption scheme, we will reference some existing cryptographic security notions, the additively homomorphic Paillier encryption scheme, and the Joye-Libert private aggregation scheme.

@@

In addition to encryption and decryption, the following homomorphic functions are provided by the Paillier scheme. $\forall m_1,m_2 \in \mathbb{Z}_N$,
\begin{align}
    \mathcal{D}(\mathcal{E}(m_1)\mathcal{E}(m_2)\!\pmod{N^2}) &= m_1+m_2\!\pmod{N} \\
    \mathcal{D}(\mathcal{E}(m_1)g^{m_2}\!\pmod{N^2}) &= m_1+m_2\!\pmod{N} \\
    \mathcal{D}(\mathcal{E}(m_1)^{m_2}\!\pmod{N^2}) &= m_1m_2\!\pmod{N}\,.
\end{align}

@@

Key generation is computed by choosing two equal length and sufficiently large primes $p$ and $q$, and computing $N=pq$. Additionally, hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}$ is defined, and the public key is set to $(N, H)$. $n$ private keys are generated by choosing $sk_i,\,1\leq i\leq n$ uniformly from $\mathbb{Z}_{N^2}$ and distributing them to all users, while the last key is set as
\begin{equation}
    sk_0 = -\sum^{n}_{i=1}sk_i \pmod{N^2}\,,
\end{equation}
and sent to the aggregator.

@@

\subsection{Linear-Combination Aggregator Oblivious Encryption}
We let a linear-combination aggregator oblivious encryption scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$. For the sake of readbility, we have ommited the time variable $t$ from values $\omega_j$ and $x_{i,j}$.

@@

\begin{description}
    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
    \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The three types of actions are:
    \begin{enumerate}
        \item \textit{Encryption:} The attacker chooses a weight $\omega$ and computes an encryption of $\omega$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(\omega)$.
        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,\mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m),x_{i,1},\dots,x_{i,m})$ such that for any two chosen combine query tuples $(i,t,\mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m),x_{i,1},\dots,x_{i,m})$ and $(i',t',\mathcal{E}_{pk_0}(\omega_1'),\dots,\mathcal{E}_{pk_0}(\omega_m'),x_{i',1}',\dots,x_{i',m}')$ the following conditions hold:
        \begin{equation*}
            t = t' \implies \mathcal{E}_{pk_0}(\omega_j) = \mathcal{E}_{pk_0}(\omega_j'),\,1\leq j\leq m
        \end{equation*}
        and
        \begin{equation*}
            i = i' \wedge t = t' \implies x_{i,m} = x_{i',m}',\,1\leq j\leq m\,.
        \end{equation*}
        They are given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}\omega_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
        \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
    \end{enumerate} 
    \item[Challenge] Next, the attacker chooses a time $t^*$, and a subset of users $U \subseteq S$ where $S$ is the complete set of users for which no combine queries for time $t^*$ and no compromise queries are made for the duration of the game. The attacker then chooses two series of tuples
    \begin{equation*}
        \langle(i,t^*,\mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m),x_{i,1},\dots,x_{i,m})\,|\,i \in U\rangle
    \end{equation*}
    and
    \begin{equation*}
        \langle(i,t^*,\mathcal{E}_{pk_0}(\omega_1'),\dots,\mathcal{E}_{pk_0}(\omega_m'),x_{i,1}',\dots,x_{i,m}')\,|\, i \in U\rangle\,,
    \end{equation*}
    and gives them to the challenger. In the case that $0 \in U$ (\textit{i.e.} the aggregator is compromised) and $U = S$, it is additionally required that
    \begin{equation*}
        \sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}\omega_j = \sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}'\omega_j'\,.
    \end{equation*}
    The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
    \begin{equation*}
        \langle\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}\omega_j)\,|\,i\in U\rangle
    \end{equation*}
    if $b=0$, or 
    \begin{equation*}
        \langle\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}'\omega_j')\,|\,i\in U\rangle
    \end{equation*}
    otherwise.
    \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requirements in the Challenge stage. That is, $U \subseteq S$.
    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of attacker $\mathcal{A}$ is defined as
    \begin{equation*}
        \mathsf{Adv}^{LCAO}(\mathcal{A}) \coloneqq \left\lvert \mathsf{Pr}[b'=b] - \frac{1}{2}\right\rvert\,.
    \end{equation*} 
\end{description}

@@

\section{Our Scheme}
%Both scheme base their security on the decisional composite residuosity assumption (DCRA)
Explain it here

Enccryption: Choose random $r$ and compute
\begin{equation}
    \mathcal{E}_{pk_0}(\omega) = (N+1)^{\omega}r^N \pmod{N^2}\,,
\end{equation}
Combine encryption:
\begin{equation}
    \begin{split}
        y^{(t)}_i &= \mathcal{E}_{pk_0,sk_i}\left(\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j\right) \\
        &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2} \\
        &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(x^{(t)}_{i,j}\omega^{(t)}_j) \pmod{N^2} \\
        &= H(t)^{sk_i}\prod^{m}_{j=1}(N+1)^{x^{(t)}_{i,j}\omega^{(t)}_j}r^N \pmod{N^2} \\
        &= H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r^N \pmod{N^2}
    \end{split}
\end{equation}
for a random $r$ (not the same as above)

Aggregation and decryption in two steps. Aggregation:
\begin{equation}
    \begin{split}
        y^{(t)} &= \prod^n_{i=1}y^{(t)}_i \pmod{N^2} \\
        &= \prod^n_{i=1}H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x_{i,j}\omega_j}r^N \pmod{N^2} \\
        &= H(t)^{\sum^n_{i=1}sk_i}\prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r^N \pmod{N^2} \\
        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r'^N \pmod{N^2}
    \end{split}
\end{equation}
for some $r' \in \mathbb{Z}_N$.

Decryption:
\begin{equation}
\sum^{n}_{i=1}\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j = \frac{L((y^{(t)})^\lambda\pmod{N^2})}{L((N+1)^\lambda\pmod{N^2})} \pmod{N}
\end{equation}

\subsection{Proof}
Give the reduction proof here for pWSAO and implicit indistinguishability of weights. Alternatively, sketch it out here and give reduction proof in the appendix.

>>>>

% User imported packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{tikz}
%\usepackage{microtype}

@@

%  .d8888b.                            888                 8888888b.                  888 d8b
% d88P  Y88b                           888                 888   Y88b                 888 Y8P
% 888    888                           888                 888    888                 888
% 888        888d888 888  888 88888b.  888888 .d88b.       888   d88P 888d888 .d88b.  888 888 88888b.d88b.
% 888        888P"   888  888 888 "88b 888   d88""88b      8888888P"  888P"  d8P  Y8b 888 888 888 "888 "88b
% 888    888 888     888  888 888  888 888   888  888      888        888    88888888 888 888 888  888  888
% Y88b  d88P 888     Y88b 888 888 d88P Y88b. Y88..88P      888        888    Y8b.     888 888 888  888  888
%  "Y8888P"  888      "Y88888 88888P"   "Y888 "Y88P"       888        888     "Y8888  888 888 888  888  888
%                         888 888
%                    Y8b d88P 888
%                     "Y88P"  888
\section{Cryptography Preliminaries} \label{sec:crypto_prelim}
When defining our system security requirements and encryption scheme, we will reference some existing cryptographic security notions, the additively homomorphic Paillier encryption scheme, and the Joye-Libert private aggregation scheme.

@@

In addition to encryption and decryption, the following homomorphic functions are provided by the Paillier scheme. $\forall m_1,m_2 \in \mathbb{Z}_N$,
\begin{align}
    \mathcal{D}(\mathcal{E}(m_1)\mathcal{E}(m_2)\!\pmod{N^2}) &= m_1+m_2\!\pmod{N} \\
    \mathcal{D}(\mathcal{E}(m_1)g^{m_2}\!\pmod{N^2}) &= m_1+m_2\!\pmod{N} \\
    \mathcal{D}(\mathcal{E}(m_1)^{m_2}\!\pmod{N^2}) &= m_1m_2\!\pmod{N}\,. \label{eqn:paillier_hom_mult}
\end{align}

@@

Key generation is computed by choosing two equal length and sufficiently large primes $p$ and $q$, and computing $N=pq$. Additionally, hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$ is defined, and the public key is set to $(N, H)$. $n$ private keys are generated by choosing $sk_i,\,1\leq i\leq n$ uniformly from $\mathbb{Z}_{N^2}$ and distributing them to all users, while the last key is set as
\begin{equation}
    sk_0 = -\sum^{n}_{i=1}sk_i \pmod{N^2}\,,
\end{equation}
and sent to the aggregator.

@@

\subsection{Linear-Combination Aggregator Oblivious Encryption} \label{subsec:lcao}
We let a linear-combination aggregator oblivious encryption scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$. For the sake of readbility, we have ommited the time variable $t$ from values $\omega_j$ and $x_{i,j}$.

@@

\begin{description}
    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
    \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The three types of actions are:
    \begin{enumerate}
        \item \textit{Encryption:} The attacker chooses a weight $\omega$ and computes an encryption of $\omega$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(\omega)$.
        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,\mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m),x_{i,1},\dots,x_{i,m})$ such that for any two chosen combine query tuples $(i,t,\mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m),x_{i,1},\dots,x_{i,m})$ and $(i',t',\mathcal{E}_{pk_0}(\omega_1'),\dots,\mathcal{E}_{pk_0}(\omega_m'),x_{i',1}',\dots,x_{i',m}')$ the following conditions hold:
        \begin{equation*}
            t = t' \implies \mathcal{E}_{pk_0}(\omega_j) = \mathcal{E}_{pk_0}(\omega_j'),\,1\leq j\leq m
        \end{equation*}
        and
        \begin{equation*}
            i = i' \wedge t = t' \implies x_{i,m} = x_{i',m}',\,1\leq j\leq m\,.
        \end{equation*}
        They are given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}\omega_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
        \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
    \end{enumerate} 
    \item[Challenge] Next, the attacker chooses a time $t^*$, and a subset of users $U \subseteq S$ where $S$ is the complete set of users for which no combine queries for time $t^*$ and no compromise queries are made for the duration of the game. The attacker then chooses two series of tuples
    \begin{equation*}
        \langle(i,t^*,\mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m),x_{i,1},\dots,x_{i,m})\,|\,i \in U\rangle
    \end{equation*}
    and
    \begin{equation*}
        \langle(i,t^*,\mathcal{E}_{pk_0}(\omega_1'),\dots,\mathcal{E}_{pk_0}(\omega_m'),x_{i,1}',\dots,x_{i,m}')\,|\, i \in U\rangle\,,
    \end{equation*}
    and gives them to the challenger. In the case that $0 \in U$ (\textit{i.e.} the aggregator is compromised) and $U = S$, it is additionally required that
    \begin{equation*}
        \sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}\omega_j = \sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}'\omega_j'\,.
    \end{equation*}
    The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
    \begin{equation*}
        \langle\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}\omega_j)\,|\,i\in U\rangle
    \end{equation*}
    if $b=0$, or 
    \begin{equation*}
        \langle\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}'\omega_j')\,|\,i\in U\rangle
    \end{equation*}
    otherwise.
    \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requirements in the Challenge stage. That is, $U \subseteq S$.
    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of attacker $\mathcal{A}$ is defined as
    \begin{equation*}
        \mathsf{Adv}^{LCAO}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
    \end{equation*} 
\end{description}

@@

\section{Our Scheme}
Our scheme is based on the Paillier and Joye-Libert schemes introduced in Section \ref{sec:crypto_prelim}, and similarly bases its security on the DCRA. As with Joye-Libert's private aggregation scheme, a trusted party is required for the initial distribution of user secret keys. Below, we give definitions for the four algorithms comprising the linear-combination aggregation encryption scheme.

\begin{description}
    \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal length, sufficiently large, primes $p$ and $q$, and compute $N=pq$. Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose an $m>1$ as the number of weights to combine, and set public parameter $\mathsf{pub}=H$, aggregator public key $pk_0 = N$ and aggregator private key $sk_0=(p,q)$. The remaining user secret keys are generated by choosing $sk_i,\,1\leq i\leq n-1$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_0 = -\sum^{n}_{i=1}sk_i \pmod{N^2}$.

    \item[$\mathsf{Enc}(pk_0, \omega)$] Encryption of weights is computed as a Paillier encryption with implicit generator $g=N+1$. This is given by
    \begin{equation}
        \mathcal{E}_{pk_0}(\omega) = (N+1)^{\omega}r^N \pmod{N^2}\,,
    \end{equation}
    for a randomly chosen $r \in \mathbb{Z}_N$.

    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m), x_{i,1},\dots,x_{i,m})$] The linear combination encryption step at time $t$ is computed as 
    \begin{equation}
        y^{(t)}_i = H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2}\,,
    \end{equation}
    and makes use of the homomorphic property \eqref{eqn:paillier_hom_mult}. Correctness follows from
    \begin{equation*}
        \begin{split}
             y^{(t)}_i &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2} \\
            &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(x^{(t)}_{i,j}\omega^{(t)}_j) \pmod{N^2} \\
            &= H(t)^{sk_i}\prod^{m}_{j=1}(N+1)^{x^{(t)}_{i,j}\omega^{(t)}_j} r^{N}_{j} \pmod{N^2} \\
            &= H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j} r_{i}^{N} \pmod{N^2}\,,
        \end{split}
    \end{equation*}
    for some values $r_i,r_j \in \mathbb{Z}_N\,,1\leq j \leq m$.

    \item[$\mathsf{AggDec}(t, pk_0, sk_0, y_1,\dots,y_n)$] Aggregation is computed as $y^{(t)} = \prod^n_{i=1}y^{(t)}_i \pmod{N^2}$, removing aggregation noise terms, and followed by Paillier decryption
    \begin{equation}
        \begin{split}
            \sum^{n}_{i=1}\sum^{m}_{j=1}&x^{(t)}_{i,j}\omega^{(t)}_j =\\
            &\frac{L((y^{(t)})^\lambda\pmod{N^2})}{L((N+1)^\lambda\pmod{N^2})} \pmod{N}\,.
        \end{split}
    \end{equation}
    The correctness of aggregation can be seen from
    \begin{align*}
        y^{(t)} &= \prod^n_{i=1}H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x_{i,j}\omega_j}r_i^N \pmod{N^2} \\
        \begin{split}
            &= H(t)^{\sum^n_{i=1}sk_i}\cdot \\
            &\qquad\qquad \prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r_i^N \pmod{N^2}
        \end{split}\\
        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r'^N \pmod{N^2}\,,
    \end{align*}
    for some values $r_i,r' \in \mathbb{Z}_N,\,1\leq i \leq n$.
\end{description}

some summary here

\subsection{Proof}
To prove the security of our introduced scheme, we recall the desired security properties of an LCAO secure scheme with IND-CPA secure encrypted weights. From the definition above, weights encrypted with public key $pk_0$ are identical to encryptions of the Paillier scheme, and therefore meet security notion IND-CPA. We omit this proof here and refer readers to the security proof of the Paillier encryption scheme \cite{} instead.

To show our scheme meets the security notion of LCAO, we prove by contrapositive that given a polynomial-time adversary $\mathcal{A}$ with non-negligible advantage $\mathsf{Adv}^{LCAO}(\mathcal{A})$ against a challenger using our scheme (\textit{i.e.} if we assume our scheme is not LCAO secure) we can construct an adversary $\mathcal{A}'$ with non-negligible advantage $\mathsf{Adv}^{AO}(\mathcal{A}')$ against a challenger using the Joye-Libert private aggregation scheme (\textit{i.e.} then the Joye-Libert scheme is not AO secure). As this is a contradiction to the Joye-Libert AO proof in \cite{}, our scheme must meet LCAO security.
\begin{pf}
    Consider adversary $\mathcal{A}$ playing the LCAO game defined in Section \ref{subsec:lcao}. The following is a construction of adversary $\mathcal{A}'$ playing the AO game from Appendix \ref{app:ao} against a challenger $\mathcal{C}$.
    \begin{description}
        \item[$\mathsf{Setup}$] $\mathcal{A}'$ receives $N$ and $H$ as public parameters from $\mathcal{C}$, and generates a new key with same size $N'=pq$ and creates aggregator public and private keys $pk_0$, $sk_0$, chooses an $m>1$, and gives $H$, $m$, and $pk_0$ to $\mathcal{A}$
        \item[$\mathsf{CombEnc}$] When $\mathcal{A}$ makes combine encryption queries $(i, t, \mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m), x_{i,1},\dots,x_{i,m})$, $\mathcal{A}'$ uses $sk_0$ to decrypt weights $\omega_1,\dots,\omega_m$ and makes an $\mathsf{Enc}(i, t, \sum^m_{j=1}x_{i,j}\omega_j)$ query to $\mathcal{C}$. The received response is of the form $(N+1)^{\sum^m_{j=1}x_{i,j}\omega_j}H(t)^{sk_i}$, from which $H(t)^{sk_i}$ is recovered by
        \begin{equation*}
            H(t)^{sk_i} = (N+1)^{\sum^m_{j=1}x_{i,j}\omega_j}H(t)^{sk_i}((N+1)^{\sum^m_{j=1}x_{i,j}})^{-1} \pmod{N^2}
        \end{equation*}
        where $^-1$ denotes the modular inverse. 
    \end{description}

    Note that decryption and encryption are polynomial in security parameter and therefore\dots
\end{pf}

% 888                            8888888b.                  888 d8b
% 888                            888   Y88b                 888 Y8P
% 888                            888    888                 888
% 888      .d88b.   .d8888b      888   d88P 888d888 .d88b.  888 888 88888b.d88b.
% 888     d88""88b d88P"         8888888P"  888P"  d8P  Y8b 888 888 888 "888 "88b
% 888     888  888 888           888        888    88888888 888 888 888  888  888
% 888     Y88..88P Y88b.         888        888    Y8b.     888 888 888  888  888
% 88888888 "Y88P"   "Y8888P      888        888     "Y8888  888 888 888  888  888
